### 2013-04-01 exam6/2.tex
Point assignment and minor tweaks.

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 20\\ \hline
2 & & 19\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 39+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\begin{problem} \pts{20}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
National Science Foundation, which requires he read and make notes on
a set of grant proposals the government is considering to fund.
Rather than read the proposals, he's decided to make a program for
modeling his notes.  His notes take the form of an outline, which
consists of a peice of text and a list of (sub)notes.  For example,
here's one of his notes (thankfully not in his handwritting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- lots of BU undergrads
\end{verbatim}

@@

\noindent
\item Write a note visitor that produces the maximum nesting depth of
  a note.  For example, the maximum nesting depth of the given example
  is 4.

@@

% \begin{verbatim}
% "1. NSF Proposal 1218390"
% "1.1. Overview"
% "1.1.1. WAT?"
% "1.1.2. Motivations"
% "1.1.2.1. unmotivating"
% "1.2. Middle (fell asleep)"
% "1.3. Conclusions"
% "1.4. Budget"
% "1.4.1. very large"
% "1.4.2. lots of BU undergrads"
% \end{verbatim}

@@

>>>>

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 20\\ \hline
2 & & 25\\ \hline
3 & & 18\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 63+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\begin{problem} \pts{25}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
National Science Foundation, which requires he read and make notes on
a set of grant proposals the government is considering to fund.
Rather than read the proposals, he's decided to make a program for
modeling his notes.  His notes take the form of an outline, which
consists of a peice of text and a list of (sub)notes.  For example,
here's one of his notes (thankfully not in his handwritting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- underfund lots of BU undergrads
\end{verbatim}

@@

\noindent
\item Design a note visitor that produces the maximum nesting depth of
  a note.  For example, the maximum nesting depth of the given example
  is 4.

@@

% \begin{verbatim}
% "1. NSF Proposal 1218390"
% "1.1. Overview"
% "1.1.1. WAT?"
% "1.1.2. Motivations"
% "1.1.2.1. unmotivating"
% "1.2. Middle (fell asleep)"
% "1.3. Conclusions"
% "1.4. Budget"
% "1.4.1. very large"
% "1.4.2. underfund lots of BU undergrads"
% \end{verbatim}

@@

\begin{problem} \pts{18}
